Increasing productivity amid stable nutrient regmines in Rhode Island Lakes and Reservoirs

### 2019-11-05 nalms_2019_talk/increasing_chla_stable_nutrients_talk.Rmd
Getting started on NALMS talk

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Background
::::::::::::::{.columns}
:::{.column}
- Nutrient managment over the years
- One goal is to reduce increased phyto
- Long-term data needed
:::
:::{.column}
content
:::
::::::::::::::

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Nutrients and Productivity
::::::::::::::{.columns}
:::{.column}
- Nutrients drive growth
- One goal is to reduce increased phyto
- Long-term data needed
:::
:::{.column}

![](figures/es-2016-02575v_0006.jpeg)

![](figures/tn_tp_chla_plot.jpg)
:::
::::::::::::::

## Nutrient Management

- What has happened with P and N reductions?
- What 
- Did it work?
